---
title: "Getting started with scStudio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with scStudio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## What scStudio is

scStudio is a local, browser-based app for interactive single-cell RNA-seq
analysis. You launch it with one command; it opens in your browser and runs all
computation on your own machine.

## Launch it

```{r}
scStudio::run_app()
```

This starts a local server and opens the app. Nothing is uploaded to any remote
server.

## Try it in 30 seconds (no data needed)

1. On the **1. Import** step, keep the source set to **Demo data**.
2. Leave the dataset as *Bundled tiny example* and click **Load demo data**.
3. Walk left to right through the steps. Each step has a "What is this step?"
   card, a method choice, adjustable thresholds, and an interactive preview.

## Use your own data

On **1. Import**, choose **Upload file** and pick:

- an `.rds` Seurat / SingleCellExperiment object,
- a 10x `.h5`, or
- a counts table (CSV/TSV; genes in rows, cells in columns).

Old Seurat objects are updated automatically. You can also fetch a file from a
URL.

## A typical run

Import → QC (adaptive MAD thresholds) → Doublet removal (scDblFinder) →
Normalize (LogNormalize) → Features + PCA → *(optional)* Integrate (Harmony) →
Cluster (Leiden) → Embed (UMAP) → Markers → Annotate (manual / SingleR /
Azimuth) → Visualize → Export.

At **Export** you can download the processed object and an R script that
reproduces every step you ran.

## Installing the heavy dependencies

The analysis engines (Seurat, scDblFinder, harmony, SingleR, ...) are optional
at install time. If a step needs a package you don't have, the app tells you what
to install. To get everything at once without managing dependencies, use the
Docker image (see the README).
